### 2022-01-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@163eb539dcb188f582e97cd285727488ed612c1e 🚀

@@

@@

>>>>

The popularity of graph embedding techniques in machine learning is
rather intuitive: while graphs are discrete objects, machine learning
techniques tend to handle continuous data better. Therefore, bringing a
discrete graph into a continuous vector space opens up a broader variety
of predictive algorithms.

\begin{longtable}[]{@{}lll@{}}
\toprule
Method & Embedded object & Reference\tabularnewline
\midrule
\endhead
DeepWalk & graph walk & Perozzi et al. (2014)\tabularnewline
node2vec & node embedding & Grover \& Leskovec (2016)\tabularnewline
\bottomrule
\end{longtable}

@@

\leavevmode\hypertarget{ref-Grover2016NodSca}{}%
Grover, A., \& Leskovec, J. (2016). Node2vec: Scalable Feature Learning
for Networks. \emph{Proceedings of the 22nd ACM SIGKDD International
Conference on Knowledge Discovery and Data Mining}, 855--864.
\url{https://doi.org/10.1145/2939672.2939754}

@@

\leavevmode\hypertarget{ref-Perozzi2014DeeOnl}{}%
Perozzi, B., Al-Rfou, R., \& Skiena, S. (2014). DeepWalk: Online
learning of social representations. \emph{Proceedings of the 20th ACM
SIGKDD International Conference on Knowledge Discovery and Data Mining},
701--710. \url{https://doi.org/10.1145/2623330.2623732}
